Issues with Dynamical Measurements Across the Disk

### 2019-02-25 paper/ms.tex
added to intro of section 4

\section{Discussion} \label{sec:discussion}
We have used high-resolution cosmologial simulations to illustrate that the ``local midplane'' defined by stellar density can have a strong azimuthal dependence, as a natural consequence of the non-axisymmetry of the Galactic disk at small scales. While this is not in itself surprising or new, we also demonstrate that extending the coordinate system established by our local midplane to a global axisymmetric coordinate system spanning the entirety of the Galactic disk introduces systematic error in computations of the actions under this symmetry assumption, when starting from the present-day positions and velocities of stars as measured, for example, by \emph{Gaia}.

While we focus our discussion now solely on the midplane, there is an
additional complication in the measurement of the distance from the Sun to the
Galactic center that may also be important. When modelling stars at Galactic
radii close to the Sun's radius, it is in principle possible to determine what
point they are orbitting about, or in other words the ``dynamic Galactic
center.'' It is not guaranteed that this dynamic Galactic center will coincide
with the distance to Sgr~A\textsuperscript{*} \citep{2018AA...615L..15G}. In
fact, \citet{2015ApJ...803...80K} were able to measure the distance of the Sun
to the Galactic center using the dynamical information of Palomar 5. Other
dynamical measurements of the Solar distance have been made, though none with
a precision capable of competing with the distance to Sgr~A\textsuperscript{*}
\citep{1981gask.book.....M,2011PASJ...63..867S,2012MNRAS.427..274S,2013AstL...39...95B,2013IAUS..289..444Z}.

>>>>

\section{Discussion} \label{sec:discussion}
We have used high-resolution cosmological simulations to illustrate that we expect the ``local midplane'' defined by stellar density to vary with azimuth by up to $\pm 100$ pc, as a natural consequence of the non-axisymmetry of the Galactic disk at small scales. While this is not in itself surprising or new, we also demonstrate that extending the coordinate system established by our local midplane to a global axisymmetric coordinate system spanning the entirety of the Galactic disk introduces systematic error in computations of the actions under this symmetry assumption, when starting from the present-day positions and velocities of stars as measured, for example, by \emph{Gaia}. These systematic errors are most important for stars on thin-disk-like orbits, where they can be large enough to yield actions representative of orbits in the thick disk. This effect is entirely due to the extension of a local to a global coordinate system, and is separate from real diffusion in stellar orbits caused by interactions with these same deviations from axisymmetry such as resonant perturbation by spiral arms or scattering from molecular clouds.

This finding has many implications for the study of the dynamics of stars in what is normally considered the regime of the epicyclic approximation: quasi-harmonic oscillations around a circular ``guiding center orbit.'' Here we consider a few of those implications, starting with an estimate of the region around the Sun where we expect an extension of the local axisymmetric coordinate system, and therefore the epicyclic approximation, to still be valid. This region is also where it should be feasible to perform ``dynamical tagging'' in the thin disk; that is, using the computed orbits or integrals of motion of field stars to match them with known open clusters.

%%%move this later - decide where
%While we focus our discussion now solely on the midplane, there is an
%additional complication in the measurement of the distance from the Sun to the
%Galactic center that may also be important. When modelling stars at Galactic
%radii close to the Sun's radius, it is in principle possible to determine what
%point they are orbiting about: the ``dynamical Galactic
%center.'' It is not guaranteed that this dynamical center will coincide
%with the distance to Sgr~A\textsuperscript{*} \citep{2018AA...615L..15G}. In
%fact, \citet{2015ApJ...803...80K} were able to measure the distance of the Sun
%to the Galactic center using the dynamical information of Palomar 5. Other
%dynamical measurements of the Solar distance have been made, though none with
%a precision capable of competing with the distance to Sgr~A\textsuperscript{*}
%\citep{1981gask.book.....M,2011PASJ...63..867S,2012MNRAS.427..274S,2013AstL...39...95B,2013IAUS..289..444Z}.
